BivData Setup

### 2020-01-23 src/BivData_Setup.Rmd
Added sis-coten to the BivData set up

```{r split.up.DF, echo=FALSE}

#SC PASS
new.Curate.FULL <- new.Curate.FULL[new.Curate.FULL$SC.pass == '1',]#10480 #9819, #9769

@@

Curated_BivData <- droplevels(Curated_BivData$strain)

@@

#add all the extra columns, blah

#percent Foci position

@@

#add telomere.dist
#str(Curated_BivData)
```

@@

#save Rdata
save.image("~./MLH1repo/data/CleanBivData_1.21.20.RData")
#save.image("data/BivData_4_PCA.RData")

>>>>

```{r split.up.DF, echo=FALSE}
#SC PASS
new.Curate.FULL <- new.Curate.FULL[new.Curate.FULL$SC.pass == '1',]#10480 #9819, #9769

@@

Curated_BivData$strain <- droplevels(Curated_BivData$strain)

@@

#add all the extra columns, blah
#percent Foci position

@@

#add telomere.dist
Curated_BivData$telo_dist <- ifelse(grepl(1, Curated_BivData$hand.foci.count), (Curated_BivData$chromosomeLength - Curated_BivData$Foci1), 
                     ifelse(grepl(2, Curated_BivData$hand.foci.count), (Curated_BivData$chromosomeLength -  Curated_BivData$Foci2), 
                     ifelse(grepl(3, Curated_BivData$hand.foci.count), (Curated_BivData$chromosomeLength - Curated_BivData$Foci3),
                    ifelse(grepl(4, Curated_BivData$hand.foci.count), (Curated_BivData$chromosomeLength - Curated_BivData$Foci4),   0))) )

Curated_BivData$telo_dist_PER <- Curated_BivData$telo_dist / Curated_BivData$chromosomeLength

#sis.co.ten
Curated_BivData <- add_SisCoTen(Curated_BivData)

@@

#save Rdata
save.image("~./MLH1repo/data/CleanBivData_1.22.20.RData")
#save.image("data/BivData_4_PCA.RData")
